### 2021-07-31 doc/thesis/chapters/results.tex
scale text better to fit in pie

In the development of a software project, the metric for the lines of code is sometimes used to give an idea of the complexity of the project.
The time it takes to implement a certain set of features can also give such an insight, even though it is a subjective metric, since it is influenced by the respective delopers experience.
However, both metrics are applied to the FM Radio Receiver project.

@@

Several parts of the system design are taken into account to analyze the lines of code, to give an impression over the largest code parts in the project.

@@

  \caption{Lines of code of the respective system design parts, presented in multiple pie charts. The percentages of code in IP design and testbench for the HLS and VHDL implementations are shown in detail.}%
  \label{fig:lines_of_code_pie_chart}%
\end{figure}

>>>>

In the development of a software project, the metric for the lines of code is sometimes used to give an idea of the scale, or volume of the project.
The time it takes to implement a certain set of features can also give such an insight and a link to the project's complexity.
It is a subjective metric though, since it is influenced by the respective developers experience in the specific application.
However, both metrics are applied to the FM Radio Receiver project.

@@

Several parts of the system design are taken into account to analyze the lines of code, to give an impression over the largest code parts in the project.
Figure \ref{fig:lines_of_code_pie_charts} shows multiple pie charts, which represent the proportions of the lines of code in the respective system design parts.

@@

  \caption{Lines of code of the respective system design parts, presented in multiple pie charts. The percentages of code in IP design and testbench for the HLS and VHDL implementations are shown in detail.}%
  \label{fig:lines_of_code_pie_charts}%
\end{figure}
